rr

### 2025-02-07 round_robin.qmd
Update round_robin.qmd

---
title: "fix rr"
format: html
editor: visual
---

@@

# Fix Round Robin Code

@@

```{r}
run_tournament <- function(num_teams, num_rounds){
  # define teams
  teams <- paste("Team", 1:num_teams)
  # put Teams and True_Strength into data frame
  team_strengths <- data.frame(
    Team = teams,
    True_Strength = qunif(1:num_teams/(num_teams+1), 0, sqrt(12)))

@@

  results <- list(average_ranks = average_ranks, k_mean = k_mean, s_mean = s_mean, simulation_list = simulation_list)

@@

```{r}
# run simulation using run_tournament() 
  # inputs are number of teams and number of rounds
results <- run_tournament(8, 1)
sims <- results$simulation_list

results
```

- run 1000 simulations for different numbers of teams
  - uniform and normal distributions for strengths
  - 3-8 teams, 16 teams

- save them as list objects

>>>>

---
title: "rr"
format: html
editor: visual
---

@@

# Round Robin Code

@@

```{r}
run_tournament <- function(num_teams=4, num_rounds=1, dist='uniform'){
  # define teams
  teams <- paste("Team", 1:num_teams)

  if (dist == "uniform"){
    stren <- qunif(1:num_teams/(num_teams+1), 0, num_teams+1)
  }
  else if (dist == "normal"){
    stren = qnorm(((1:num_teams) - 0.5) / num_teams, 0, 1)
  }

  # put Teams and True_Strength into data frame
  team_strengths <- data.frame(
    Team = teams,
    True_Strength = stren)

@@

  results <- list(average_ranks = average_ranks, k_mean = k_mean, s_mean = s_mean, simulation_list = simulation_list, all_k = kendallcor, all_s = spearmancor)

@@

```{r}
# run simulation using run_tournament() 
  # inputs are number of teams and number of rounds
results <- run_tournament(8, 1, "uniform")
sims <- results$simulation_list

# results
```

-   run 1000 simulations for different numbers of teams
    -   uniform and normal distributions for strengths
    -   3-8 teams, 16 teams
-   save them as list objects

## Correlation Coefficients Histograms

```{r}
hist(results$all_k, main = "Kendall Cor Dist", xlab = "Kendall Correlation")
hist(results$all_s, main = "Spearman Cor Dist", xlab = "Spearman Correlation")
```
